\documentclass[11pt]{article}

\usepackage{fancyhdr}
\usepackage[letterpaper]{geometry}
\usepackage[latin2]{inputenc}
\usepackage{graphicx}
\usepackage{ulem}
\usepackage{amsmath}

\pagestyle{fancyplain}
\lhead{\large{CSE 015: Discrete Mathematics}}
\rhead{\large{Fall Semester 2017}}

\title{\bf Homework Assignment 5\\Diffie-Hellman Key Exchange}
\date{Sunday, November 19 2017}
\author{Pedro Damian Sanchez Jr}

\begin{document}

\maketitle

\section*{Private Key}

Assume $A = g^a$ mod $p$.

\section*{Public Keys}

Assume $p$ = 9433, and, $g$ = 5.

\section*{Exchange}

Transmission $A =1218$ is recieved.

\section*{Question 1}

What do you need to send me, in order for us to complete the exchange of the key? Show all your work.

\section*{Question 1 Solution}

Assume $B = g^b$ mod $p$; if I choose $b = 6$ then:

\begin{displaymath}
\begin{tabular}{c}
$B = (5)^{(6)}$ mod $9433$\\$ = 15625$ mod $9433$\\$ = 6192$\\
\end{tabular}
\end{displaymath}

Once I transmit $B = 6192$ we must both arrive at the same $"s"$ by computing the that [$s = A^b$ mod $p$] for me, and, [$s = B^a$ mod $p$] for you.

\section*{Question 2}

If Trudy, the intruder and Eve, the eavesdropper have intercepted all the our communications above, how would they go about recovering the key that we exchanged? Be very specific.

\section*{Question 2 Solution}

Since the private keys $"a"$ and $"b"$ aren't known to either Trudy or Eve, they would first have to compute the value of either of those two keys to decrypt all future transmissions.

\section*{Question 3}

(Bonus question) What is the value of my private key $a$? How much work was required to find it?

\section*{Question 3 Solution}

\begin{displaymath}
\begin{tabular}{c}
Private Key $a = 681$
\end{tabular}
\end{displaymath}

To find that value, an algorithm must be implemented to test all numbers between 1 and 9433.

\end{document}
